Future challenges for Research Software Engineering

### 2025-04-17 future_challenges_for_RSEng.tex
fixes

\section{The Situation}
In order to give a more explicit setting, imagine a world ten years from now.
Not too much, to be overwhelmingly far in the future, but distant enough for some changes to occur.
Over this timeframe Kim\cite{Anzt2021} and Kay\cite{competencies-F1000}
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sunset blessed beach.
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are persisting, where they are now happy that a younger generation is now taking up the baton and carries forward their work.
What issues have newly emerged, where they are now just happy to say: “Oh well… My successor takes care of that”.
\begin{story}{Introduction}{intro}
In order to bring this future to life these two personas will accompany us and we will shed light on certain aspects
of their future in respective small story boxes.
 \end{story}

>>>>

\section{The Situation}
In order to give a more explicit setting, imagine a world ten years from now.
Not too much, to be overwhelmingly far in the future, but distant enough for some changes to occur.
Over this timeframe Kim\cite{Anzt2021} and Kay\cite{Goth2024}
were able to ride the waves of their career in Research Software Engineering and are now pondering early retirement on a sunset blessed beach.
But the world has moved on.
When they look back, what will they see as problems which are now solved?
Which tasks are persisting, where they are now happy that a younger generation is now taking up the baton and carries forward their work.
What issues have newly emerged, where they are now just happy to say: “Oh well… My successor takes care of that”.
\begin{story}{Introduction}{intro}
In order to bring this future to life these two personas will accompany us and we will shed light on certain aspects
of their future in respective small story boxes.
 \end{story}
